Classless Java: Tuning Java Interfaces

### 2015-12-03 paper/sections/CaseStudy.tex
more revise and compress

\begin{figure}
\begin{tabular}{l|l}
\lstinputlisting[linerange=34-41]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT
&
\lstinputlisting[linerange=50-56]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
\end{tabular}
\caption{The Expression Problem. Initial system on the left, and code for adding
  print operation on the right. }\label{fig:ep}
\end{figure}\bruno{Yanlin: code is overflowing the margins. Note that
  there are 2 spare lines that can be used on the right!}

@@

\lstinputlisting[linerange=80-82]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=INDEPENDENT_EXTENSIBILITY

>>>>

\begin{figure}
\begin{tabular}{l|l}
\lstinputlisting[linerange=34-41]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT
&
\lstinputlisting[linerange=50-57]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
\end{tabular}
\caption{The Expression Problem (left: initial system, right: code for adding
  print operation).}\label{fig:ep}
\end{figure}% \bruno{Yanlin: code is overflowing the margins. Note that
  % there are 2 spare lines that can be used on the right!}

@@

\lstinputlisting[linerange=81-83]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=INDEPENDENT_EXTENSIBILITY

### 2015-12-03 paper/sections/Formalization.tex
more revise and compress

\noindent
What happens if a new interface \Q@M@ extends one \Q@A@${}_i$ and one
\Q@B@${}_j$? Nine representative cases are shown next:\\*
\noindent
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{M extends} & \textbf{A1}                  & \textbf{A2} & \textbf{A3} \\ \hline
\textbf{B1}        & conservative error                        & conflict error      & conservative error       \\ \hline
\textbf{B2}        & both abstract, accepted                        & conservative error       & both abstract, accepted       \\ \hline
\textbf{B3}        & \textbf{conservative error} &conflict  error       & conservative error      \\ \hline
\end{tabular}
\\*
We try to classify the results in the table:
\begin{itemize}
\item \textbf{conflict error} happens when the methods from are both implemented, which is also an error in most trait models.
\item \textbf{both abstract, accepted} happens when the methods from are both abstract, which is also considered correct in all
  trait models.
\item \textbf{conservative error} happens when only one method from is implemented, which is different from what we would expect in
  a trait model, but is coherent with the conservative idea that a method
  defined in an interface should not silently satisfy a method in another one.
\end{itemize}

>>>>

\noindent
What happens if a new interface \Q@M@ extends one \Q@A@${}_i$ and one
\Q@B@${}_j$? Nine representative cases are shown next:\\*
\noindent
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{M extends} & \textbf{A1}                  & \textbf{A2} & \textbf{A3} \\ \hline
\textbf{B1}        & conservative error                        & conflict error      & conservative error       \\ \hline
\textbf{B2}        & both abstract, accepted                        & conservative error       & both abstract, accepted       \\ \hline
\textbf{B3}        & \textbf{conservative error} &conflict  error       & conservative error      \\ \hline
\end{tabular}
\\*
We try to classify the results in the table:
\begin{itemize}
\item \textbf{conflict error} happens when the methods from both are implemented, which is also an error in most trait models.
\item \textbf{both abstract, accepted} happens when the methods from both are abstract, which is also considered correct in all
  trait models.
\item \textbf{conservative error} happens when only one method is implemented
  (leaving another one abstract), which is different from what we would expect in
  a trait model, but is coherent with the conservative idea that a method
  defined in an interface should not silently satisfy a method in another one.
\end{itemize}

### 2015-12-03 paper/sections/FutureWork.tex
more revise and compress

\subsection{Qualifiers in Methods} %{Private state
The biggest limitation of our approach is the inability to model qualifiers
for class methods (private, protected, synchronized, etc.). For example, the absence
of the support for private/protected methods in Java8 interfaces forces all
members of interfaces to be public, including static methods. Since we use
abstract methods to encode the state, our state is always all public. Still, because 
the state can only be accessed by methods, it 
is impossible for the user to know if a certain method maps directly to a field
or if it has a default implementation.  If the user wants a constructor that
does not directly maps to the fields, (as for secondary constructors in Scala)
he can simply define its own \Q@of@ method and delegate on the generated one, as
in
\begin{lstlisting}
@Obj interface Point{  int x(); int y();
  static Point of(int val){return Point.of(val,val);}  }
\end{lstlisting}
However, the generated \Q@of@ method would also be present and public.  If a
future version of Java was to support \emph{static private methods in
  interfaces} we could extend our code generation to handle also encapsulation.
Currently, it is possible to use a public nested class with private static
methods inside, but this is ugly and cumbersome. One possibility is that the
annotation processor takes methods with a \Q!@Private! annotation, and turns it into
static private methods of a nested class. In this extension, also the \Q@of@
method could be made private following the same pattern.

>>>>

\subsection{Qualifiers in Methods} %{Private state
The biggest limitation of our approach is the inability to model qualifiers
for class methods (private, protected, synchronized, etc.). For example, the absence
of the support for private/protected methods in Java 8 interfaces forces all
members of interfaces to be public, including static methods. Since we use
abstract methods to encode state, our state is always all public. Still, because 
the state can only be accessed by methods, it 
is impossible for the user to know if a certain method maps directly to a field
or if it has a default implementation.  If the user wants a constructor that
does not directly maps to the fields, (as for secondary constructors in Scala)
he can simply define its own \Q@of@ method and delegate on the generated one:
\begin{lstlisting}
@Obj interface Point{  int x(); int y();
  static Point of(int val){return Point.of(val,val);}  }
\end{lstlisting}
However, the generated \Q@of@ method would also be present and public.  If a
future version of Java was to support \emph{static private methods in
  interfaces} we could extend our code generation to handle also encapsulation.
Currently, it is possible to use a public nested class with private static
methods inside, but this is ugly and cumbersome. One possibility is that the
annotation processor takes methods with a \Q!@Private! annotation, and turns it into
static private methods of a nested class. In this extension, also the \Q@of@
method could be made private following the same pattern.
